\vskip-0.6in Trade Agreements in the Shadow of Lobbying\protect\footnote{Formerly circulated under the title ``Trade Agreements, Lobbying and Separation of Powers''}

### 2016-02-01 letter.tex
add paragraph to letter on E2; add more to E3 para

Editor's point $\#$3: Thank you for the suggestion to add an extensive form and to define the game more clearly and formally. I think the addition of the normal form in Figure 1 made this portion of the paper, in the new subsections 2.1 (The Basic Setup) and 2.2 (Preferences) significantly more readable. I hope you will agree.

>>>>

Editor's point $\#$2: I have created four subsections within Section 2 to structure the exposition of the model. I think this is much clearer than the previous draft.

Editor's point $\#$3: Thank you for the suggestion to add an extensive form and to define the game more clearly and formally. I think the addition of the normal form in Figure 1 made this portion of the paper significantly more readable. I hope you will agree. The discussion of the players, timing, and the presentation of the extensive form are at the end of Section 2.1 (The Basic Setup). I largely allow the extensive form to do the work of laying out the strategy spaces so as not to clutter the text. The payoffs are gathered together in their own section (2.2: Preferences).
